A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-01 paper/paper.tex
Plot tweaks

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}

@@

\paragraph{No labels, undirected}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-cumulative.pdf}
    \caption{MCS Plain instances, cumulative runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, cumulative runtimes}
\end{figure}

\paragraph{Vertex and edge labels, directed}

\paragraph{No labels, undirected, connected}

\paragraph{Vertex and edge labels, connected}

\paragraph{Large subgraph isomorphism instances}

\paragraph{Compared to CP FC}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Nodes}
\end{figure}

>>>>

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cleveref}

@@

\paragraph{No labels, undirected} are in \cref{figure:plain-cumulative}.

\paragraph{Vertex and edge labels, directed} are in \cref{figure:33ved-cumulative}.

\paragraph{No labels, undirected, connected} have yet to be run.

\paragraph{Vertex and edge labels, connected} have yet to be run.

\paragraph{Large subgraph isomorphism instances} have yet to be run.

\paragraph{Compared to CP FC} Runtimes are in \cref{figure:plain-james-versus-cp-fc-scatter} and \cref{figure:33ved-james-versus-cp-fc-scatter}, and nodes are in \cref{figure:plain-james-versus-cp-fc-nodes-scatter} and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-cumulative.pdf}
    \caption{MCS Plain instances, cumulative runtimes}\label{figure:plain-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, cumulative runtimes}\label{figure:33ved-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Runtimes (TODO?? heatmapify this)}\label{figure:plain-james-versus-cp-fc-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Runtimes (TODO?? heatmapify this)}\label{figure:33ved-james-versus-cp-fc-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Nodes (TODO?? heatmapify this)}\label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}
